% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt

\usepackage{hyperref}
\usepackage{pifont}
%\usepackage{CJKutf8}
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=9in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Jos\'e Hiram Soltren}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{Hiring Managers\\
Cloudera Inc.\\
1001 Page Mill Road, Building 3\\ 
Palo Alto, CA 94304-1009}
    
\begin{flushleft}
{\LARGE\sffamily Jos\'e Hiram Soltren}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill 1201 West Park Street, Cedar Park, TX 78613-2801 \\
\hfill \ding{41} \href{mailto:jsoltren@alum.mit.edu}{jsoltren@alum.mit.edu}
       \ding{38} +1 (347) 503-9558 \\
\hfill \ding{43} \url{https://www.linkedin.com/in/jsoltren}
\end{flushright} 
\vfill % forces letterhead to top of page

 
\opening{Dear Hiring Managers:} 
 
%\noindent PARAGRAPH ONE: State reason for letter, name the position or type 
%of work you are applying for and identify source from  which  you 
%learned   of   the  opening.  (i.e.  Career  Development  Center, 
%newspaper, employment service, personal contact). 

Cloudera is at the forefront of distributed systems work in the cloud age.
It seems like a great place to be.
 
%\noindent PARAGRAPH  TWO:  Indicate why you are interested in the position, 
%the company, its products, services - above all, stress what  you 
%can  do  for  the employer. If you are a recent graduate, explain 
%how your academic background makes you a qualified candidate  for 
%the  position.  If  you have practical work experience, point out 
%specific achievements or unique qualifications. Try not to repeat 
%the  same  information  the reader will find in the resume. Refer 
%the reader to the enclosed resume or application which summarizes 
%your  qualifications,  training,  and experiences. The purpose of 
%this section is to strengthen your resume  by  providing  details 
%which bring your experiences to life. 

At present, I am a System Software Engineer at NVIDIA. I work on the Linux
Graphics Driver with an emphasis on video decoding and post processing. My
work is very close to the hardware. I work closely with hardware teams and
architects as well as end users to ensure a great experience.

On the surface, there would seem to be little crossover between driver work
and work on Apache Hadoop. I conjecture that there is very good alignment
between the two. Both problem spaces concern themselves with parallelism,
scheduling, determinism, scalability, and even power. Both rely on locking,
atomicity, and concurrency to dispatch work. Both benefit from many layers
of knowledge, down to the hardware. I believe that the lessons that I have
learned from GPU driver work and elsewhere would be an excellent contribution
to Cloudera's strategy.
 
%\noindent PARAGRAPH THREE: Request a personal interview and  indicate  your 
%flexibility as to the time and place. Repeat your phone number in 
%the letter and offer assistance to help in a speedy response. For 
%example,  state that you will be in the city where the company is 
%located on a certain date and would like to set up an  interview. 
%Or,  state  that  you  will  call  on a certain date to set up an 
%interview. End the letter by thanking  the  employer  for  taking 
%time to consider your credentials. 

I am sending this cover letter and r\'esum\'e because I believe that
growth, and particularly kaizen (
%\begin{CJK}{UTF8}{min}改善\end{CJK}, 
continuous improvement) are important. For Cloudera, this means hiring
strong engineers from a variety of disciplines who can frame problems in
novel ways leading to novel solutions. Personally, this means pursuing
growth in new directions. The timing is good for me to consider my next
move after nearly five years at NVIDIA.

Michal Ostrowski is a friend who encouraged me to submit this application.
He should be considered a referrer. I've also been in contact with
Philip Langdale through my work on the VDPAU stack at NVIDIA. Philip and
Michal, as it happens, have worked together for some time. Both have
encouraged me to submit this application.

If there is a potential for a good fit, I hope to speak with you further.
At present, I am located in the Austin, TX region and am unable to relocate.
(Though, an occasional visit to Palo Alto is welcome.)

Thank you for your consideration.
 
\closing{Sincerely yours,} 
 

 
\encl{Current r\'esum\'e}  				% Enclosures

\end{letter}
 

\end{document}






