% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}
\usepackage{pifont}

\begin{document}

\name{Jos\'e Hiram Soltren}
% \address used twice to have two lines of address
\address{1201 West Park Street, Cedar Park, TX 78613-2801}
\address{\ding{41}\href{mailto:jsoltren@alum.mit.edu}{jsoltren@alum.mit.edu}
         \ding{38}(347) 503-9558
         \ding{43}\url{https://www.linkedin.com/in/jsoltren}}

 
\begin{resume}
 
\section{SYNOPSIS}
System Software Engineer and MIT alum. \textbf{Ten years’ experience}
in various areas:\\
Linux, kernel development, device drivers, computer graphics, firmware,\\
video decoding, end user software, and systems administration.\\
Additional specialties: automotive, aviation, machining, CAD, CAM, cycling.
 
% \sl will be bold italic in New Century Schoolbook (or
% any postscript font) and just slanted in
% Computer Modern (default) font
 
\section{EDUCATION}

\textbf{Massachusetts Institute of Technology, Cambridge, MA} \\
\\
{\sl Master of Engineering,} Electrical Engineering and Computer Science
\hfill Aug 2009
\begin{itemize}  \itemsep -2pt % reduce space between items
\item Course work in operating systems, biomedical informatics, network
      protocols, scientific computation, signal processing, power electronics.
\item Wrote thesis on using Semantic Web technologies to determine privacy
      policy compliance of database queries using a rules-based reasoner.
\end{itemize} 
{\sl Bachelor of Science,} Electrical Engineering and Computer Science
\hfill Jun 2007
\begin{itemize}  \itemsep -2pt % reduce space between items
\item Minor in Science, Technology, and Society.
\end{itemize}

\section{EXPERIENCE}
\textbf{Senior System Software Engineer} \\
NVIDIA Corporation, Santa Clara, CA and Austin, TX \hfill May 2011 -\\
Member of elite team responsible for the proprietary NVIDIA graphics driver stack for
Linux, FreeBSD, and Solaris.
Technical lead - Video Decode and Post-Processing API for UNIX (VDPAU)
Ported VDPAU to a brand new video decoder architecture.
Added support for next generation H.265/HEVC hardware video decode to the Linux
driver and to VDPAU. (See: https://github.com/NVIDIA/vdpau-hevc-example)
Participate in hardware architectural reviews for video decoding hardware.
Responsible for video post processing shaders in Cg and GLSL languages.
Expertise in OpenGL multithreading, graphics pipeline configuration, rendering state.
Key member of new hardware bringup process:
o Communication with hardware, software, and chip delivery teams;
o Prepared test plans and programs to execute on pre-silicon software and
hardware emulation environments;
o Execution of test programs on early silicon in first days of bringup
Debug and fix critical stop-ship issues related to video decoding on GPUs.
Technologies used: C, C++, Python, Makefile; gcc, gdb, Linux kernel, NVIDIA GPUs,
OpenGL, firmware/microcodes.
 
\section{COMPUTER \\ SKILLS} {\sl Languages \& Software:} COBOL, IFPS, Focus, 
         Megacalc, Pascal, Modula2, C, APL, SNOBOL, 
                FORTRAN, LISP, SPIRES, BASIC, VSPC Autotab, 
                IBM 370 Assembler, Lotus 1-2-3. \\
                {\sl Operating Systems:} MTS, TSO, Unix.
 
\section{EXPERIENCE} {\sl Business Applications Programmer} \hfill Fall 1990 \\
                Allied-Signal Bendix Friction Materials Division, 
                Financial Planning Department, Latham, NY
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Developed four "user friendly" forecasting 
                    systems each of which produces 18 to 139 
                    individual reports. 
                \item   Developed or improved almost all IFPS 
                    programs used for financial reports. 
                \end{itemize}
 
                {\sl Research Programmer} \hfill            Summer 1990 \\
                Psychology Department, Rensselaer Polytechnic 
                Institute 
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Performed computer aided statistical analysis 
                    of data. 
                 \end{itemize} 
                {\sl Assistant Manager} \hfill        Summers 1988-89 \\
                Thunder Restaurant, Canton, CT
                  \begin{itemize}
                   \item Recognized need for, developed, and wrote 
                    employee training manual. Performed various 
                    duties including cooking, employee training, 
                    ordering, and inventory control. 
                   \end{itemize} 
 
\section{COMMUNITY \\ SERVICE}  Organized and directed the 1988 and 1989 Grand 
                 Marshall Week \newline ``Basketball Marathon.'' A 24 hour 
                charity event to benefit the Troy Boys Club. Over 
                250 people participated each year. 

\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
            Elected {\it House Manager}, Rho Phi Sorority \\
            Elected {\it Sports Chairman} \\
            Attended Krannet Leadership Conference \\
                Headed delegation to Rho Phi Congress \\
                Junior varsity basketball team \\
                Participant, seven intramural athletic teams 
 

\end{resume}
\end{document}







