% LaTeX resume using res.cls
\documentclass[line,margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{hyperref}
\usepackage{pifont}
\usepackage{fancyhdr}

\pagestyle{fancy}
%\lhead{Jos\'e Hiram Soltren}
\cfoot{1201 West Park Street, Cedar Park, TX 78613-2801 \\
  \ding{41} \href{mailto:jsoltren@alum.mit.edu}{jsoltren@alum.mit.edu}
  \ding{38} +1 (347) 503-9558\\\ding{43} \url{https://www.linkedin.com/in/jsoltren}}

\begin{document}
\thispagestyle{empty}

\name{Jos\'e Hiram Soltren}
% \address used twice to have two lines of address
\address{1201 West Park Street, Cedar Park, TX 78613-2801}
\address{\ding{41} \href{mailto:jsoltren@alum.mit.edu}{jsoltren@alum.mit.edu}
  \ding{38} +1 (347) 503-9558
  \ding{43} \url{https://www.linkedin.com/in/jsoltren}}

\begin{resume}

\section{Synopsis}
System Software Engineer and MIT alum. \textbf{Ten years’ experience}
in various areas:\\
Linux, kernel development, device drivers, computer graphics, firmware,\\
video decoding, end user software, and systems administration.\\
Additional specialties: automotive, aviation, machining, CAD, CAM, cycling.

% \textit will be bold italic in New Century Schoolbook (or
% any postscript font) and just slanted in
% Computer Modern (default) font

\input{resources/education.tex}

\section{Experience}

\textbf{Senior System Software Engineer} \\
NVIDIA Corporation, Santa Clara, CA and Austin, TX \hfill May 2011 - present
\begin{itemize}  \itemsep -2pt % reduce space between items
\item Member of elite team responsible for the proprietary NVIDIA graphics
      driver stack for Linux, FreeBSD, and Solaris.
\item Technical lead - Video Decode and Post-Processing API for UNIX (VDPAU).
\item Ported VDPAU to a brand new video decoder architecture.
\item Added support for next generation H.265/HEVC hardware video decode to
      the Linux driver and to VDPAU.
      \url{https://github.com/NVIDIA/vdpau-hevc-example}
\item Participate in hardware architectural reviews for video decoding hardware.
\item Responsible for video post processing shaders in Cg and GLSL languages.
\item Expertise in OpenGL multithreading, graphics pipeline configuration,
      rendering.
\item Key member of new hardware bringup process:
    \begin{itemize}  \itemsep -2pt % reduce space between items
    \item Communication with hardware, software, and chip delivery teams.
    \item Preparation test plans and programs to execute on pre-silicon
          software and hardware emulation environments.
    \item Execution of test programs on early silicon in first days of bringup.
    \end{itemize}
\item Debug and fix critical stop-ship issues related to video decoding on GPUs.
\item \textit{Technologies used: C, C++, Python, Makefile; gcc, gdb, Linux
              kernel, NVIDIA GPUs, OpenGL, firmware/microcodes.}
\end{itemize}

\textbf{Member of Technical Staff} \\
Model N, Redwood Shores, CA \hfill Aug 2009 - Nov 2010
\begin{itemize}  \itemsep -2pt % reduce space between items
\item Member of middleware team, writing pricing, contracts, customer,
      compliance, and commitments software for pharmaceutical and
      semiconductor industries.
\item Technical ownership of key contract pricing feature in product.
\item Worked with customers and management to define and prioritize features.
\item Implemented customer facing features in both back-end application server
      (Java) and front-end user interface (JavaScript).
\item \textit{Technologies used: Java, JavaScript, Oracle SQL; Apache Tomcat,
              Oracle\\\mbox{WebLogic}, IBM WebSphere, Oracle SQL Server.}
\end{itemize}

\newpage
% There should be a page break here.

{ \sffamily Jos\'e Hiram Soltren} \\

\section{Experience}

\textbf{Systems Administrator} \\
D. E. Shaw \& Co., L.P., New York, NY \hfill Jun 2007 - Jun 2008
\begin{itemize}  \itemsep -2pt % reduce space between items
\item D. E. Shaw \& Co. is a global investment management firm located in NYC.
\item Member of Systems team, responsible for all desktop, server, networking,
      and communications hardware and software infrastructure.
\item Provided direct end user support through Systems Helpdesk rotations.
\item Served as liaison between front office and Systems engineering
      specialists.
\item Drove user requests and tickets to completion.
\item Designed, and managed building of, video conferencing rooms.
\end{itemize}


\section{Community}
\textbf{Weekend Residential Faculty} \\
Eastside College Preparatory School, East Palo Alto, CA \hfill Aug 2012 - Jul 2013
\begin{itemize}  \itemsep -2pt % reduce space between items
\item Operated weekend dormitory program for high school students.
\end{itemize}

\textbf{Big Brother} \\
Big Brothers and Big Sisters of the Bay Area, Milpitas, CA \hfill Jan 2011 - Dec 2012
\begin{itemize}  \itemsep -2pt % reduce space between items
\item Served as friend and mentor to a young man through his formative years.
\end{itemize}

\textbf{Trip Leader} \\
Bike \& Build, Inc., Brooklyn, NY and Philadelphia, PA \hfill Jan 2006 - Aug 2008
\begin{itemize}  \itemsep -2pt % reduce space between items
\item Planned and led two cross-country charity bicycle tours for young adults.
\end{itemize}


%\section{HOBBIES}
%Bicycle repair and maintenance. \\
%Reverse engineering, repair, and sale of vintage computer keyboards. \\
%Metal and machine work.


\section{Languages}
Fluent in: English, Spanish, C.\\
Proficient in: OpenGL, Java, JavaScript, R, C++, Scheme, Perl, Python, PHP,\\
\mbox{MATLAB}, Cg, GLSL, CUDA.

\section{Citizenship}
United States

\end{resume}
\end{document}







