About Me::

\begin{itemize}
\item I'm a software engineer focusing on low level system software.
\item I have a proven track record of successes in personal and professional projects in this domain.
\item I tend to focus on the backend and on fundamentals, but care deeply about the whole product.
\item I believe in simplicity, elegance, and beauty at every level of engineering design.
\item I believe software engineers have much to learn from aeronautical engineers.
\item I believe in Net Neutrality and a right to privacy, and oppose censorship of non-hateful speech.
\item I believe that worrying about job titles makes us lose sight of the real problems to be solved.
\item I taught myself BASIC and circuits at age eight (so fun!).
\item I'm Hispanic (Puerto Rican) and a New Yorker.
\item I'm an alumnus of Stuyvesant and MIT, in both cases as one of the only Puerto Ricans.
\item I'm a maker, a tinkerer, a hacker, a commercial pilot, a husband and a father.
\end{itemize}

What I've Done::

\begin{itemize}
\item Brought joy to millions of households by bringing Roku players to market.
\item Tackled our most challenging scaling problems for deep learning hardware at Intel AI.
\item Worked on the core of Apache Spark, and have spoken publicly about my work.
\item Worked on the NVIDIA Linux graphics driver, and owned the video decoder for a while.
\item Designed a new type of computer keyboard, shipped it, and sold over 1200 to date.
\item Along the way, I've solved thousands of problems and unblocked countless people.
\end{itemize}

Everywhere I go, I decrease overhead, and add value and simplicity far above my pay grade.\\
I leave things cleaner than I found them, whether or not they are mine to clean.

What I Want To Do::

\begin{itemize}
\item Be a key teammate at a top-tier computer hardware/software firm.
\item Work on world-class problems with world-class people in a world-class environment.
\item Continue to grow every day.
\item Lead by example.
\end{itemize}

Check my r\'esum\'e for more details on my current and former position(s).\\
\emph{Fit is more important than experience.}
